---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# coronavirusbrazil

<!-- badges: start -->
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
[![GitHub commit](https://img.shields.io/github/last-commit/mralbu/coronavirusbrazil)](https://github.com/mralbu/coronavirusbrazil/commit/master)
<!-- badges: end -->

The coronavirusbrazil package provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic for Brazil. The raw data pulled from [Ministério da Saúde](https://covid.saude.gov.br/) and [brasil.io](https://brasil.io/dataset/covid19/caso).

This repository was inspired by the [RamiKrispin/coronavirus](https://github.com/RamiKrispin/coronavirus) package repository.


## Installation

You can install the released version of coronavirusbrazil from [CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("devtools")
devtools::install_github("mralbu/coronavirusbrazil")
```

## Usage

The package contains the following datasets:

```{r example}
library(coronavirusbrazil)


data("coronavirus_br")
head(coronavirus_br) 
```

```{r, warning=FALSE, message=FALSE}
plot_coronavirus_br(coronavirus_br, xaxis_br = "cases", delta = TRUE, log_scale = TRUE)
```

```{r, warning=FALSE, message=FALSE}
data("coronavirus_br_states")
head(coronavirus_br_states) 
```

```{r, warning=FALSE}
plot_coronavirus_states(coronavirus_br_states, filter_state = c("RJ", "SP", delta = TRUE, log_scale = TRUE))
```


```{r}
data("coronavirus_br_cities")
head(coronavirus_br_cities) 
```

There are also geospatial datasets avaiable:

```{r}
dplyr::glimpse(spatial_br_states)
#plot(spatial_br_states)
```

```{r}
dplyr::glimpse(spatial_br_cities)
#plot(spatial_br_states)
```

# Data Sources

- States: [Ministério da Saúde](https://covid.saude.gov.br/)
- Cities: [brasil.io](https://brasil.io/dataset/covid19/caso)
